Incentivizing Exploration with Unbiased History

### 2018-11-02 intro.tex
Working on the intro ...

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust the system to implement the mechanism that it claims to implement). However, these assumptions are quite problematic when the disclosure policy selectively withholds information, \eg recommends randomly chosen actions to some randomly selected agents (which is a major technique in the prior work).

We take a step back and re-examine these assumptions. We ask: How would users interpret messages/recommendations generated by a disclosure policy? More importantly, how to design disclosure policies that would be interpreted by users in a predictable way, while ensuring good exploration-exploitation balance? Without the standard assumptions, which conceptual frameworks can be used to reason about the user response to a disclosure policy in precise terms?

@@

\ascomment{stopped for the day ...}

>>>>

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement). However, these assumptions appear quite problematic in the context of recommendation systems. In particular, disclosure policies studied in prior work merely recommend an action to each agent, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users. This works out extremely well in theory, but it is very unclear whether users would trust the principal to implement the stated policy and, even if they do, whether they would react to it rationally. Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement, whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration. Furthermore, regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.

\ascomment{stable text up to here.}

@@
